A Switching Planner for Combined Task and Observation Planning

### 2011-02-09 subarchitectures/planner.sa/trunk/src/latex/AAAI11/conc.tex
new conclusion

\vspace{-1ex}

For use in an integrated continual planning and execution monitoring
system on a mobile robot platform, we developed a planner that
switches between fast sequential and expensive DT planning. Given a
DTPDDL model of the environment, sequential planning is used to
compute an initial deterministic sequential plan and complementary
runtime evolution of the decision process. That plan is executed until
testing of an assumption about the runtime state is scheduled. At that
point a DT session performs some sensing which determines whether or
not the sequential session should be allowed to continue, or otherwise
acts to achieve the overall objectives. We find our approach performs
quickly and relatively efficiently in a number of large real-world
task and observation planning problems.

>>>>

%\vspace{-1ex}

We have addressed a key challenge, specifically that of high-level
continual planning and execution monitoring for efficient
deliberations according to rich probabilistic models afforded by
recent integrated robotic systems. We developed a system that can plan
quickly given large realistic probabilistic models, by switching
between: (a) fast sequential planning, and (b) expensive DT planning
in small abstractions of the problem at hand. Sequential and DT
planning is interleaved, the former identifying a rewarding sequential
plan in the underlying process, and the latter solving small sensing
problems posed during sequential plan execution.
%%
We have evaluated our system in large real-world task and
observation planning problems, finding that it performs quickly
and relatively efficiently.

%% We developed a continual planning and execution monitoring
%% system for use on a mobile robot platform. .
%% %%
%% Our planner switches between: (a) fast sequential planning, and (b)
%% expensive DT planning in small abstractions of the problem at
%% hand. Our approach addresses a key challenge put to the community, by
%% Planning for a DTPDDL model of the environment, sequential and DT
%% sessions are interleaved, the former identifying a rewarding plan, and
%% the latter solving practically sized sensing problems posed during
%% serial plan executions execution.
%% %%
%% Our system answers a key challenge, with {\em probabilistic} --i.e., {\em quantitative}--
%% models of noisy sensing and state.

%% is used to compute an
%% sequential plans and complementary runtime evolutions of the
%% decision process. That plans are executed until the outcome of the next
%% action scheduled for execution is too uncertain. At that point a DT
%% session performs sensing that can help determine how the sequential
%% plan might evolve, or otherwise acts to achieve the goals. We find our
%% approach performs quickly and relatively efficiently in a number of
%% large real-world task and observation planning problems.
